\documentclass[11pt,a4paper]{article}

\usepackage[margin=1.6cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage{parskip}

\definecolor{accent}{HTML}{B07A2E}
\definecolor{muted}{HTML}{555555}
\definecolor{ink}{HTML}{1A1A1A}

\hypersetup{
    colorlinks=true,
    urlcolor=accent,
    linkcolor=accent
}

\pagestyle{empty}
\setlength{\parindent}{0pt}

\titleformat{\section}
  {\normalfont\fontsize{9}{11}\bfseries\color{accent}\MakeUppercase}
  {}{0em}{}[\vspace{-2pt}\hrule height 0.4pt\vspace{4pt}]
\titlespacing*{\section}{0pt}{10pt}{4pt}

\newcommand{\role}[3]{%
  \textbf{#1} \hfill \textcolor{muted}{\small #3}\\%
  \textcolor{muted}{\small #2}%
}

\newcommand{\edublock}[4]{%
  \textbf{#1} \hfill \textcolor{muted}{\small #3}\\%
  \textcolor{muted}{\small #2}%
  \ifx&#4&\else\\\textcolor{muted}{\small #4}\fi%
}

\color{ink}

\begin{document}

\begin{center}
{\fontsize{22}{26}\selectfont\bfseries Alex Nikolaenko}\\[4pt]
\textcolor{muted}{\small
  \href{mailto:al.nikolaenko@outlook.com}{al.nikolaenko@outlook.com}
  \quad\textbar\quad
  \href{https://github.com/Legard525}{github.com/Legard525}
  \quad\textbar\quad
  \href{https://t.me/Legard_l}{t.me/Legard\_l}
  \quad\textbar\quad
  \href{https://legard525.github.io}{legard525.github.io}
}
\end{center}

\vspace{2pt}

\section{Profile}
Mathematician by training, builder by instinct. Dual BSc in Mathematics and Economics (HSE Moscow $\cdot$ University of London International Programme), heading to LSE for an MSc in Financial Mathematics in September 2026. Comfortable across stochastic calculus, time-series econometrics, and the engineering side of quantitative work --- from short-rate calibration to building agentic LLM workflows.

\section{Education}

\edublock{MSc Financial Mathematics}{London School of Economics and Political Science}{Sep 2026 --- }{}

\vspace{4pt}

\edublock{BSc Mathematics \& Economics \textit{(Dual Degree)}}{HSE Moscow $\cdot$ University of London International Programme}{2022 --- 2026}{GPA 9.24/10 $\cdot$ top 0.6\% of cohort}

\vspace{4pt}

\edublock{Secondary School}{Moscow School No.~57 --- Mathematics and Economics class}{2015 --- 2022}{}

\section{Experience}

\role{Junior Business Analyst}{T-Bank}{Feb --- Apr 2026}
\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=1pt]
  \item Translated business requirements into engineering specifications; coordinated between product stakeholders and development teams.
  \item Built practical foundation in system architecture and project management within a large-bank tech environment.
\end{itemize}

\role{Student Mentor \& Tutor}{HSE Moscow}{2025 --- 2026}
\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=1pt]
  \item Onboarding and year-round support for incoming first-year students.
  \item Voluntary Macroeconomics~II tutoring sessions for peers.
\end{itemize}

\section{Selected Projects}

\textbf{CS:GO / CS2 Skin Price Analysis} \hfill \textcolor{muted}{\small Python $\cdot$ ARMA--GARCH $\cdot$ Cointegration}\\
Modelled log-price dynamics of in-game cosmetics; identified volatility clustering, fat tails, and seasonality. Applied Zivot--Andrews structural-break detection and Engle--Granger cointegration to find co-moving skin pairs --- demonstrating statistical parallels with traditional financial assets.

\vspace{4pt}

\textbf{MOEX G-Curve Modelling} \hfill \textcolor{muted}{\small Python $\cdot$ Short-rate Models $\cdot$ EVT/GPD $\cdot$ MLE}\\
Calibrated Vasicek, Cox--Ingersoll--Ross, and Hull--White short-rate models to Russian government bond data via maximum likelihood. Fitted return-distribution tails with the Generalised Pareto Distribution; assessed goodness-of-fit through empirical-vs-theoretical quantile coverage.

\section{Skills}

\textbf{Programming} \quad Python $\cdot$ R $\cdot$ SQL $\cdot$ \LaTeX\\
\textbf{Tools} \quad Git $\cdot$ Pandas $\cdot$ NumPy $\cdot$ SciPy $\cdot$ PyTorch $\cdot$ Docker\\
\textbf{Quant \& Finance} \quad Stochastic calculus $\cdot$ Time series $\cdot$ Linear algebra $\cdot$ Risk modelling\\
\textbf{AI \& Agents} \quad Claude Code $\cdot$ Anthropic SDK $\cdot$ MCP server integration $\cdot$ Multi-agent orchestration

\section{Languages}

Russian --- native \quad\textbar\quad\ English --- fluent

\end{document}
